# What's this?

-   It calculates the correlation between footfall and (1) number of connected wards -- indicating connectivity and (2) travelling time between wards and footfall locations
-   It includes the Pearson's correlation test and T-test
-   It shows the relationship as indicated by the Pearson's Correlation coefficient and p-value that either rejects or accepts null hypothesis

# Load required package

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
# install.packages("ggpubr")
library(ggpubr)
```

# Load requried csv

```{r}
mon_corr_connect_wards <- read_csv(here::here("ff_access_connectwards_mon.csv"))
mon_corr_tt <- read_csv(here::here("ff_access_avg_tt.csv"))

tue_corr_connect_wards <- read_csv(here::here("ff_access_connectedwards_tue.csv"))
tue_corr_tt <- read_csv(here::here("ff_access_avg_tt_tue.csv"))

wed_corr_connect_wards <- read_csv(here::here("ff_access_connectwards_wed.csv"))
wed_corr_tt <- read_csv(here::here("ff_access_avgtt_wed.csv"))

thurs_corr_connect_wards <- read_csv(here::here("ff_access_connectedwards_thurs.csv"))
thurs_corr_tt <- read_csv(here::here("ff_access_avgtt_thurs.csv"))

fri_corr_connect_wards <- read_csv(here::here("ff_access_connectedwards_fri.csv"))
fri_corr_tt <- read_csv(here::here("ff_access_avgtt_fri.csv"))

sat_corr_connect_wards <- read_csv(here::here("ff_access_connectedwards_sat.csv"))
sat_corr_tt <- read_csv(here::here("ff_access_avgtt_sat.csv"))

sun_corr_connect_wards <- read_csv(here::here("ff_connectedwards_sun.csv"))
sun_corr_tt <- read_csv(here::here("ff_access_avgtt_sun.csv"))
```

# Correlation between ff and number of connected wards

## Monday

```{r}
# Monday
ggplot(mon_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Monday") +
  theme_minimal()
```

```{r}
# Calculate correlation coefficient
correlation_mon_connect <- cor(mon_corr_connect_wards$no_connected_wards, mon_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_mon_connect))

```

## Tue

```{r}
ggplot(tue_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Tuesday") +
  theme_minimal()
```

```{r}
# Calculate correlation coefficient
correlation_tue_connect <- cor(tue_corr_connect_wards$no_connected_wards, tue_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_tue_connect))

```

## Wed

```{r}
ggplot(wed_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Wednesday") +
  theme_minimal()
```

```{r}
# Calculate correlation coefficient
correlation_wed_connect <- cor(wed_corr_connect_wards$no_connected_wards, wed_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_wed_connect))

```

## Thurs

```{r}
ggplot(thurs_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Thursday") +
  theme_minimal()
```

```{r}
# Calculate correlation coefficient
correlation_thurs_connect <- cor(thurs_corr_connect_wards$no_connected_wards, thurs_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_thurs_connect))
```

## Fri

```{r}
ggplot(fri_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Friday") +
  theme_minimal()
```

```{r}
correlation_fri_connect <- cor(fri_corr_connect_wards$no_connected_wards, fri_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_fri_connect))
```

## Sat

```{r}
# Sat
ggplot(sat_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of conencted wards",
       title = "Saturday") +
  theme_minimal()
```

```{r}
correlation_sat_connect <- cor(sat_corr_connect_wards$no_connected_wards, sat_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_sat_connect))
```

## Sun

```{r}
# Sun
ggplot(sun_corr_connect_wards, aes(x = no_connected_wards, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Number of connected wards",
       title = "Sunday") +
  theme_minimal()
```

```{r}
correlation_sun_connect <- cor(sun_corr_connect_wards$no_connected_wards, sun_corr_connect_wards$ff_count)
print(paste("Correlation coefficient:", correlation_sun_connect))
```

------------------------------------------------------------------------

# Correltaion between ff and avg travelling time

## Mon

```{r}
ggplot(mon_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Monday") +
  theme_minimal()
```

```{r}
correlation_mon_avgtt <- cor(mon_corr_tt$avg_tt, mon_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_mon_avgtt))

```

## Tue

```{r}
ggplot(tue_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Tuesday") +
  theme_minimal()
```

```{r}
correlation_tue_avgtt <- cor(tue_corr_tt$avg_tt, tue_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_tue_avgtt))

```

## Wed

```{r}
ggplot(wed_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Wednesday") +
  theme_minimal()
```

```{r}
correlation_wed_avgtt <- cor(wed_corr_tt$avg_tt, wed_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_wed_avgtt))
```

## Thurs

```{r}
ggplot(thurs_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Thursday") +
  theme_minimal()
```

```{r}
correlation_thurs_avgtt <- cor(thurs_corr_tt$avg_tt, thurs_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_thurs_avgtt))
```

## Fri

```{r}
ggplot(fri_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Friday") +
  theme_minimal()
```

```{r}
correlation_fri_avgtt <- cor(fri_corr_tt$avg_tt, fri_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_fri_avgtt))
```

## Sat

```{r}
ggplot(sat_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Saturday") +
  theme_minimal()
```

```{r}
correlation_sat_avgtt <- cor(sat_corr_tt$avg_tt, sat_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_sat_avgtt))
```

## Sun

```{r}
ggplot(sun_corr_tt, aes(x = avg_tt, y = ff_count)) +
  geom_point(color = "blue") +  # Scatter plot
  geom_smooth(method = "lm", color = "red") + # regression line
  stat_cor(method = "pearson") +
  labs(x = "Footfall Count",
       y = "Average travelling time",
       title = "Sunday") +
  theme_minimal()
```

```{r}
correlation_sun_avgtt <- cor(sun_corr_tt$avg_tt, sun_corr_tt$ff_count)
print(paste("Correlation coefficient:", correlation_sun_avgtt))
```

```{r}
p_sun_avgtt <- summary(sun_corr_tt$coefficients["x", "Pr(>|t|)"])
print(p_sun_avgtt)
```
