# What's this?

-   R package that calculates travel time matrix
-   An indicator of accessibility across London

```{r}
install.packages("r5r")
options(java.parameters = "-Xmx2G")
install.packages("akima")

install.packages("gtfs2gps")
```

# Loading library package

```{r}
library(r5r)
library(sf)
library(ggplot2)
library(data.table)
library(osmdata)
library(dplyr)
library(tidyverse)
library(tmap)
library(leaflet)
library(mapview)
library(rJava)
library(janitor)
library(akima)
library(gtfs2gps)
```

<https://ipeagit.github.io/intro_access_book/3_calculando_acesso.en.html>

```{r}
options(java.parameters = "-Xmx32G")
```

## Setting up network in r package

```{r}
path = ("/Users/wingkaho/Desktop/UCL/CASA0004_Dissertation/CASA0004_DissTest/DissTest/r5r_data")
r5r_core <- setup_r5(data_path = path)
```

# Data wrangling

```{r}
# Loading london footfall location data (csv file)
london_ff <- read.csv(here::here("london_ff.csv"))
location <- read.csv(here::here("CDRC", "UWB_Metadata_ONLINE.csv"), header = TRUE, sep = ",", encoding = "latin1", na = " ")
location <- location %>%
  dplyr::rename(instsigid = "InstSigID") %>%
  clean_names()
location <- location %>%
  filter(instsigid %in% c("100027", "100059", "100065", "100070", "100072", 
                          "100081", "100087", "100088", "100089", "100091", 
                          "100092", "100095", "100098")) %>%
  clean_names()

# Loading shapefile of boroughs, wards, and lsoas + calculate centroids of them to get the origin location for accessibility matrix
boroughs <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))
boroughs %>% mapview()
wards <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "London_Ward.shp"))
wards %>% mapview()
#lsoas <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "LSOA_2011_London_gen_MHW.shp"))
#lsoas %>% mapview()

# Reprojecting file onto the same projection
london_location_points <- location %>%
  drop_na(longitude, latitude) %>%
  st_as_sf(., coords = c("longitude", "latitude"),
           crs = 4326)

coords <- st_coordinates(london_location_points)
london_location_points <- london_location_points %>%
  mutate(longitude = coords[, 1],
         latitude = coords[, 2])


boroughs <- boroughs %>%
  st_transform(., 4326)
wards <- wards %>%
  st_transform(., 4326)
wards
#lsoas <- lsoas %>%
  #st_transform(., 4326)

# Take a centroid
wards_centroid <- wards %>%
  st_centroid() %>%
  st_geometry()
ggplot() + 
  geom_sf(data = boroughs, fill = 'white') +
  geom_sf(data = boroughs_centroid, color = 'red')
wards_centroid <- wards %>%
  st_centroid() %>%
  st_geometry()
ggplot() +
  geom_sf(data = wards, fill = 'white') +
  geom_sf(data = wards_centroid, color = 'red')

boroughs_with_centroids <- boroughs %>%
  mutate(centroid_long = st_coordinates(boroughs_centroid)[,1],
         centroid_lat = st_coordinates(boroughs_centroid)[,2])

wards_with_centroids <- wards %>%
  mutate(centroid_long = st_coordinates(wards_centroid)[,1],
         centroid_lat = st_coordinates(wards_centroid)[,2])

boroughs_with_centroid_df <- data.frame(boroughs_with_centroids)
wards_with_centroid_df <- data.frame(wards_with_centroids)


```

# Setting up poi for calculation

```{r}
dest_ff_location <- london_location_points %>%
  select(street, longitude, latitude)
ori_wards <- wards_with_centroids %>%
  select(GSS_CODE, centroid_long, centroid_lat)
ori_boroughs <- boroughs_with_centroids %>%
  select(NAME, centroid_long, centroid_lat)

ori_boroughs$NAME<- str_replace_all(ori_boroughs$NAME, " ", "") %>%
  str_to_lower()
ori_wards$NAME <- str_replace_all(ori_wards$NAME, " ", "") %>%
  str_to_lower()
dest_ff_location$street <- str_replace_all(dest_ff_location$street, " ", "") %>%
  str_to_lower()
```

# Export csv for accessibility matrix calculation

```{r}
# Export as csv ready for accessibility matrix calculation
#write.csv(dest_ff_location, file = "dest_test_accessibility_matrix.csv", row.names = FALSE)
#write.csv(ori_boroughs, file = "boroughs_ori_centroids_accessibility_matrix.csv", row.names = FALSE)
write.csv(ori_wards, file = "ori_wards_centroids_accessibility_matrix.csv", row.names = FALSE)
```

# Start

```{r}
ori_boroughs_point <- read_csv(here::here("ori_boroughs_accessibility_matrix.csv"))
ori_boroughs_point <- na.omit(ori_boroughs_point)
ori_wards_point <- read_csv(here::here("ori_wards_gss_code.csv"), show_col_types = FALSE)
dest_ff_point <- read_csv(here::here("dest_test_accessibility_matrix.csv"))
ori_wards_point <- drop_na(ori_wards_point)


# Find duplicated rows
duplicate_rows <- ori_wards_point[duplicated(ori_wards_point) | duplicated(ori_wards_point, fromLast = TRUE), ]

# Display duplicated rows
print(duplicate_rows)

```

# Result

*date* - Monday: 31 Jan - Tuesday: 12 April - Wednesday: 16 March - Thursday: 3 March - Friday: 11 Feb - Saturday: 5 Feb - Sunday: 20 March

*time* - Morn: 10:00 - Noon: 12:00 - Afternoon: 14:00 - Evening: 19:00 - Midnight: 00:00 AND 03:00 (test the differences between night tube and non night tube day)

*mode* - Transit - Subway - Rail - Bus - Tram - Ferry - Cable Car - Walk - Car

## All time series (same weekday and same departure time but different months)

-   to show the accessibility throughout the months didnt change much that affect the footfall as a whole.

### Weekday

### Jan 24 1400

```{r}

mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("24-01-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
jan_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### Feb 21 1400

```{r}
# Noon 12:00
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("21-02-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
feb_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### 20 March 1400

```{r}
# Afternoon 14:00
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-03-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
march_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### April 17 1400

```{r}
# Night 19:00
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-04-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
apr_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### Weekend

### Jan 27 1400

```{r}
# Midnight 00:00
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("27-01-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
jan_weekend_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### Feb 17 1400

```{r}
# Midnight 03:00
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-02-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
feb_weekend_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### March 16 1400

```{r}
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("16-03-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
march_weekend_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

### April 20

```{r}
mode <- "TRANSIT"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-04-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
apr_weekend_ttm <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(jan_ttm, file = "jan_ttm.csv", row.names = TRUE)
write.csv(feb_ttm, file = "feb_ttm.csv", row.names = TRUE)
write.csv(march_ttm, file = "march_ttm.csv", row.names = TRUE)
write.csv(apr_ttm, file = "apr_ttm.csv", row.names = TRUE)
write.csv(jan_weekend_ttm, file = "jan_weekend_ttm.csv", row.names = TRUE)
write.csv(feb_weekend_ttm, file = "feb_weekend_ttm.csv", row.names = TRUE)
write.csv(march_weekend_ttm, file = "march_weekend_ttm.csv", row.names = TRUE)
write.csv(apr_weekend_ttm, file = "apr_weekend_ttm.csv", row.names = TRUE)
```

## Monday 22 Jan (short travel time)

### Transit

```{r}
# Morn 10:00
mode <- ("TRANSIT")
#max_walk_time <- 30 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("22-01-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
mon_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
# Afternoon 14:00
mode <- ("TRANSIT")
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("22-01-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
mon_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
# Night 19:00
mode <- ("TRANSIT")
#max_walk_time <- 0 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("22-01-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
mon_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
# Midnight 00:00
mode <- ("TRANSIT")
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("22-01-2024 00:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
mon_midnight_0000_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
# Midnight 03:00
mode <- ("TRANSIT")
# max_walk_time <- 30 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("22-01-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
mon_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
map(unique(mon_morn_transit_1$mode), function(m) {
  #map(unique(access_df$cutoff), function(c, m) {
    p <- access_df %>%
      filter(mode == m) %>%
      left_join(wards, by = c("from_id" = "GSS_CODE")) %>%
      ggplot(aes(fill=travel_time_p50/1000)) +
      geom_sf(aes(geometry=geom), size=0.2) +
      coord_sf(datum=NA) +
      scale_fill_distiller(palette = "Spectral") +
      labs(fill = "Accessibility\nJobs (x1000)") +
      theme_light() +
      theme(legend.position = "right") +
      labs(title = "Accessibility to Jobs in the GLA",
           subtitle = paste0("mode = ", m, ", travel time cutoff = ", c, " minutes"))
    
    ggsave(plot = p, filename = file.path(path,paste0("map_gla_", m) ), 
           dpi = 300, width = 20, height = 15, units = "cm")

})
```

```{r}
mon_morn_transit_1 %>%
  left_join(wards, by = c("from_id"="GSS_code")) %>%
  arrange(travel_time_p50) %>%
  ggplot(aes(fill=travel_time_p50)) +
  geom_sf(aes(geometry=geom), color=NA) +
  scale_fill_distiller(palette = "Spectral") +
  facet_grid(mode~cutoff)

access_sf <- left_join(wards, mon_morn_transit_1, by = c("from_id"="GSS_code")) 
```

#### Export ttm

```{r}
write.csv(mon_morn_transit_1, file = "mon_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(mon_afternoon_transit_1, file = "mon_afternoon_transit_1.csv", row.names = TRUE)
write.csv(mon_night_transit_1, file = "mon_night_transit_1.csv", row.names = TRUE)
write.csv(mon_midnight_0000_transit_1, file = "mon_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(mon_midnight_0300_transit_1, file = "mon_midnight_0300_transit_1.csv", row.names = TRUE)
```

#### Avg travelling time for each location

*mon morn*

```{r}
# Subset 
bgs_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_mon_morn_transit_1 <- mon_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_mon_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_mon_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_mon_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

*noon*

```{r}
bgs_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_mon_noon_transit_1 <- mon_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")

# Avg tt 
mean(bgs_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_mon_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_mon_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_mon_noon_transit_1$travel_time_p50, na.rm = TRUE) 
```

*night*

```{r}
bgs_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_mon_night_transit_1 <- mon_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")

# Avg tt 
mean(bgs_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_mon_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_mon_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_mon_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_mon_midnight_transit_1 <- mon_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")

# Avg tt 
mean(bgs_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_mon_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
```

*sat morn*

```{r}
# Subset 
bgs_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sat_morn_transit_1 <- sat_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sat_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sat_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sat_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

*noon*

```{r}
# Subset 
bgs_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sat_noon_transit_1 <- sat_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sat_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sat_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sat_noon_transit_1$travel_time_p50, na.rm = TRUE) 
```

*night*

```{r}
# Subset 
bgs_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sat_night_transit_1 <- sat_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sat_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sat_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sat_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

*midnight*

```{r}
# Subset 
bgs_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sat_midnight_transit_1 <- sat_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sat_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_tue_morn_transit_1 <- tue_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_tue_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_tue_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_tue_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_tue_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_tue_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_tue_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_tue_noon_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_tue_night_transit_1 <- tue_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_tue_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_tue_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_tue_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_tue_midnight_transit_1 <- tue_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_tue_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_wed_morn_transit_1 <- wed_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_wed_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_wed_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_wed_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_wed_noon_transit_1 <- tue_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_wed_noon_transit_1 <- wed_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_wed_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_wed_noon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_wed_noon_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_wed_night_transit_1 <- wed_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_wed_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_wed_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_wed_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_wed_midnight_transit_1 <- wed_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_wed_midnight_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_thurs_morn_transit_1 <- thurs_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_thurs_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_thurs_afternoon_transit_1 <- thurs_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_thurs_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_thurs_night_transit_1 <- thurs_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_thurs_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_thurs_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_thurs_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_thurs_midnight_0300_transit_1 <- thurs_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_thurs_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_fri_morn_transit_1 <- fri_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_fri_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_fri_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_fri_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_fri_afternoon_transit_1 <- fri_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_fri_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_fri_night_transit_1 <- fri_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_fri_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_fri_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_fri_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_fri_midnight_0300_transit_1 <- fri_midnight_0300_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_fri_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sun_morn_transit_1 <- sun_morn_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sun_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sun_morn_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sun_morn_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sun_afternoon_transit_1 <- sun_afternoon_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sun_afternoon_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sun_night_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sun_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sun_night_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sun_night_transit_1$travel_time_p50, na.rm = TRUE) 
```

```{r}
bgs_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "brucegrovesouth")
chsm_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "claphamhighstreetmiddle")
crm_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "claphamroadmiddle")
dw_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "danelandwalk")
ern_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadnorth")
ers_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "edgwareroadsouth")
hrm_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "highroadmiddle")
krm_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "kenningtonroadmiddle")
nrs_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "norwoodroadsouth")
osw_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "oxfordstreetwest")
shrm_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "streathamhighroadmiddle")
tb_sun_midnight_0300_transit_1 <- sun_midnight_0300_transit_1 %>%
  filter(to_id == "thebroadway")
wrs_sun_midnight_0300_transit_1 <- sun_night_transit_1 %>%
  filter(to_id == "wandsworthroadsouth")
# Avg tt 
mean(bgs_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(chsm_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(crm_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(dw_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(ern_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(ers_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(hrm_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(krm_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(nrs_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(osw_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(shrm_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
mean(tb_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE)
mean(wrs_sun_midnight_0300_transit_1$travel_time_p50, na.rm = TRUE) 
```

## Tuesday 20 Feb

### Transit

```{r}

mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-02-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
tue_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-02-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
tue_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-02-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
tue_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("20-02-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
tue_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(tue_morn_transit_1, file = "tue_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(tue_afternoon_transit_1, file = "tue_afternoon_transit_1.csv", row.names = TRUE)
write.csv(tue_night_transit_1, file = "tue_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(tue_midnight_0300_transit_1, file = "tue_midnight_0300_transit_1.csv", row.names = TRUE)
```

### Wednesday 13 March

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("13-03-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
wed_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("13-03-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
wed_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("13-03-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
wed_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("13-03-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
wed_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(wed_morn_transit_1, file = "wed_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(wed_afternoon_transit_1, file = "wed_afternoon_transit_1.csv", row.names = TRUE)
write.csv(wed_night_transit_1, file = "wed_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(wed_midnight_0300_transit_1, file = "wed_midnight_0300_transit_1.csv", row.names = TRUE)
```

### Thursday 18 April

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("18-04-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
thurs_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("18-04-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
thurs_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("18-04-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
thurs_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("18-04-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
thurs_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(thurs_morn_transit_1, file = "thurs_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(thurs_afternoon_transit_1, file = "thurs_afternoon_transit_1.csv", row.names = TRUE)
write.csv(thurs_night_transit_1, file = "thurs_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(thurs_midnight_0300_transit_1, file = "thurs_midnight_0300_transit_1.csv", row.names = TRUE)
```

### Friday 26 Jan

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("26-01-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
fri_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("26-01-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
fri_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("26-01-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
fri_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("26-01-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
fri_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(fri_morn_transit_1, file = "fri_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(fri_afternoon_transit_1, file = "fri_afternoon_transit_1.csv", row.names = TRUE)
write.csv(fri_night_transit_1, file = "fri_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(fri_midnight_0300_transit_1, file = "fri_midnight_0300_transit_1.csv", row.names = TRUE)
```

### Saturday 17 Feb

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-02-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sat_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-02-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sat_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-02-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sat_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("17-02-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sat_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(sat_morn_transit_1, file = "sat_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(sat_afternoon_transit_1, file = "sat_afternoon_transit_1.csv", row.names = TRUE)
write.csv(sat_night_transit_1, file = "sat_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(sat_midnight_0300_transit_1, file = "sat_midnight_0300_transit_1.csv", row.names = TRUE)
```

### Sunday 30 March

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("30-03-2024 10:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sun_morn_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("30-03-2024 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sun_afternoon_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("30-03-2024 19:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sun_night_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

```{r}
mode <- "transit"
# max_walk_time <- 60 # minutes
max_trip_duration <- 60 # minutes
departure_datetime <- as.POSIXct("30-03-2024 03:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

# calculate a travel time matrix
sun_midnight_0300_transit_1 <- travel_time_matrix(r5r_core = r5r_core,
                          origins = ori_wards_point,
                          destinations = dest_ff_point,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          # max_walk_time = max_walk_time,
                          max_trip_duration = max_trip_duration)
```

#### Export ttm

```{r}
write.csv(sun_morn_transit_1, file = "sun_morn_transit_1.csv", row.names = TRUE)
#write.csv(mon_noon_transit_1, file = "mon_noon_transit_1.csv", row.names = TRUE)
write.csv(sun_afternoon_transit_1, file = "sun_afternoon_transit_1.csv", row.names = TRUE)
write.csv(sun_night_transit_1, file = "sun_night_transit_1.csv", row.names = TRUE)
#write.csv(tue_midnight_0000_transit_1, file = "tue_midnight_0000_transit_1.csv", row.names = TRUE)
write.csv(sun_midnight_0300_transit_1, file = "sun_midnight_0300_transit_1.csv", row.names = TRUE)
```

# Count the number of connected wards to each ff lcoation

```{r}
sum(mon_morn_transit_1$to_id == "brucegrovesouth")
sum(mon_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(mon_morn_transit_1$to_id == "claphamroadmiddle")
sum(mon_morn_transit_1$to_id == "danelandwalk")
sum(mon_morn_transit_1$to_id == "edgwareroadnorth")
sum(mon_morn_transit_1$to_id == "edgwareroadsouth")
sum(mon_morn_transit_1$to_id == "highroadmiddle")
sum(mon_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(mon_morn_transit_1$to_id == "norwoodroadsouth")
sum(mon_morn_transit_1$to_id == "oxfordstreetwest")
sum(mon_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(mon_morn_transit_1$to_id == "thebroadway")
sum(mon_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(mon_afternoon_transit_1$to_id == "brucegrovesouth")
sum(mon_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(mon_morn_transit_1$to_id == "claphamroadmiddle")
sum(mon_afternoon_transit_1$to_id == "danelandwalk")
sum(mon_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(mon_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(mon_afternoon_transit_1$to_id == "highroadmiddle")
sum(mon_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(mon_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(mon_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(mon_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(mon_afternoon_transit_1$to_id == "thebroadway")
sum(mon_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(mon_night_transit_1$to_id == "brucegrovesouth")
sum(mon_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(mon_night_transit_1$to_id == "claphamroadmiddle")
sum(mon_night_transit_1$to_id == "danelandwalk")
sum(mon_night_transit_1$to_id == "edgwareroadnorth")
sum(mon_night_transit_1$to_id == "edgwareroadsouth")
sum(mon_night_transit_1$to_id == "highroadmiddle")
sum(mon_night_transit_1$to_id == "kenningtonroadmiddle")
sum(mon_night_transit_1$to_id == "norwoodroadsouth")
sum(mon_night_transit_1$to_id == "oxfordstreetwest")
sum(mon_night_transit_1$to_id == "streathamhighroadmiddle")
sum(mon_night_transit_1$to_id == "thebroadway")
sum(mon_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(mon_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(mon_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(mon_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(mon_midnight_0300_transit_1$to_id == "danelandwalk")
sum(mon_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(mon_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(mon_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(mon_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(mon_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(mon_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(mon_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(mon_midnight_0300_transit_1$to_id == "thebroadway")
sum(mon_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(tue_morn_transit_1$to_id == "brucegrovesouth")
sum(tue_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(tue_morn_transit_1$to_id == "claphamroadmiddle")
sum(tue_morn_transit_1$to_id == "danelandwalk")
sum(tue_morn_transit_1$to_id == "edgwareroadnorth")
sum(tue_morn_transit_1$to_id == "edgwareroadsouth")
sum(tue_morn_transit_1$to_id == "highroadmiddle")
sum(tue_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(tue_morn_transit_1$to_id == "norwoodroadsouth")
sum(tue_morn_transit_1$to_id == "oxfordstreetwest")
sum(tue_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(tue_morn_transit_1$to_id == "thebroadway")
sum(tue_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sat_morn_transit_1$to_id == "brucegrovesouth")
sum(sat_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(sat_morn_transit_1$to_id == "claphamroadmiddle")
sum(sat_morn_transit_1$to_id == "danelandwalk")
sum(sat_morn_transit_1$to_id == "edgwareroadnorth")
sum(sat_morn_transit_1$to_id == "edgwareroadsouth")
sum(sat_morn_transit_1$to_id == "highroadmiddle")
sum(sat_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(sat_morn_transit_1$to_id == "norwoodroadsouth")
sum(sat_morn_transit_1$to_id == "oxfordstreetwest")
sum(sat_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(sat_morn_transit_1$to_id == "thebroadway")
sum(sat_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sat_afternoon_transit_1$to_id == "brucegrovesouth")
sum(sat_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(sat_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(sat_afternoon_transit_1$to_id == "danelandwalk")
sum(sat_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(sat_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(sat_afternoon_transit_1$to_id == "highroadmiddle")
sum(sat_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(sat_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(sat_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(sat_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(sat_afternoon_transit_1$to_id == "thebroadway")
sum(sat_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sat_night_transit_1$to_id == "brucegrovesouth")
sum(sat_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(sat_night_transit_1$to_id == "claphamroadmiddle")
sum(sat_night_transit_1$to_id == "danelandwalk")
sum(sat_night_transit_1$to_id == "edgwareroadnorth")
sum(sat_night_transit_1$to_id == "edgwareroadsouth")
sum(sat_night_transit_1$to_id == "highroadmiddle")
sum(sat_night_transit_1$to_id == "kenningtonroadmiddle")
sum(sat_night_transit_1$to_id == "norwoodroadsouth")
sum(sat_night_transit_1$to_id == "oxfordstreetwest")
sum(sat_night_transit_1$to_id == "streathamhighroadmiddle")
sum(sat_night_transit_1$to_id == "thebroadway")
sum(sat_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sat_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(sat_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(sat_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(sat_midnight_0300_transit_1$to_id == "danelandwalk")
sum(sat_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(sat_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(sat_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(sat_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(sat_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(sat_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(sat_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(sat_midnight_0300_transit_1$to_id == "thebroadway")
sum(sat_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(tue_morn_transit_1$to_id == "brucegrovesouth")
sum(tue_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(tue_morn_transit_1$to_id == "claphamroadmiddle")
sum(tue_morn_transit_1$to_id == "danelandwalk")
sum(tue_morn_transit_1$to_id == "edgwareroadnorth")
sum(tue_morn_transit_1$to_id == "edgwareroadsouth")
sum(tue_morn_transit_1$to_id == "highroadmiddle")
sum(tue_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(tue_morn_transit_1$to_id == "norwoodroadsouth")
sum(tue_morn_transit_1$to_id == "oxfordstreetwest")
sum(tue_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(tue_morn_transit_1$to_id == "thebroadway")
sum(tue_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(tue_afternoon_transit_1$to_id == "brucegrovesouth")
sum(tue_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(tue_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(tue_afternoon_transit_1$to_id == "danelandwalk")
sum(sat_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(tue_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(tue_afternoon_transit_1$to_id == "highroadmiddle")
sum(tue_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(tue_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(tue_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(tue_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(tue_afternoon_transit_1$to_id == "thebroadway")
sum(tue_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(tue_night_transit_1$to_id == "brucegrovesouth")
sum(tue_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(tue_night_transit_1$to_id == "claphamroadmiddle")
sum(tue_night_transit_1$to_id == "danelandwalk")
sum(tue_night_transit_1$to_id == "edgwareroadnorth")
sum(tue_night_transit_1$to_id == "edgwareroadsouth")
sum(tue_night_transit_1$to_id == "highroadmiddle")
sum(tue_night_transit_1$to_id == "kenningtonroadmiddle")
sum(tue_night_transit_1$to_id == "norwoodroadsouth")
sum(tue_night_transit_1$to_id == "oxfordstreetwest")
sum(tue_night_transit_1$to_id == "streathamhighroadmiddle")
sum(tue_night_transit_1$to_id == "thebroadway")
sum(tue_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(tue_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(tue_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(tue_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(tue_midnight_0300_transit_1$to_id == "danelandwalk")
sum(tue_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(tue_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(tue_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(tue_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(tue_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(tue_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(tue_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(tue_midnight_0300_transit_1$to_id == "thebroadway")
sum(tue_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(wed_morn_transit_1$to_id == "brucegrovesouth")
sum(wed_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(wed_morn_transit_1$to_id == "claphamroadmiddle")
sum(wed_morn_transit_1$to_id == "danelandwalk")
sum(wed_morn_transit_1$to_id == "edgwareroadnorth")
sum(wed_morn_transit_1$to_id == "edgwareroadsouth")
sum(wed_morn_transit_1$to_id == "highroadmiddle")
sum(wed_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(wed_morn_transit_1$to_id == "norwoodroadsouth")
sum(wed_morn_transit_1$to_id == "oxfordstreetwest")
sum(wed_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(wed_morn_transit_1$to_id == "thebroadway")
sum(wed_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(wed_afternoon_transit_1$to_id == "brucegrovesouth")
sum(wed_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(wed_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(wed_afternoon_transit_1$to_id == "danelandwalk")
sum(wed_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(wed_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(wed_afternoon_transit_1$to_id == "highroadmiddle")
sum(wed_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(wed_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(wed_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(wed_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(wed_afternoon_transit_1$to_id == "thebroadway")
sum(wed_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(wed_night_transit_1$to_id == "brucegrovesouth")
sum(wed_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(wed_night_transit_1$to_id == "claphamroadmiddle")
sum(wed_night_transit_1$to_id == "danelandwalk")
sum(wed_night_transit_1$to_id == "edgwareroadnorth")
sum(wed_night_transit_1$to_id == "edgwareroadsouth")
sum(wed_night_transit_1$to_id == "highroadmiddle")
sum(wed_night_transit_1$to_id == "kenningtonroadmiddle")
sum(wed_night_transit_1$to_id == "norwoodroadsouth")
sum(wed_night_transit_1$to_id == "oxfordstreetwest")
sum(wed_night_transit_1$to_id == "streathamhighroadmiddle")
sum(wed_night_transit_1$to_id == "thebroadway")
sum(wed_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(wed_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(wed_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(wed_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(wed_midnight_0300_transit_1$to_id == "danelandwalk")
sum(wed_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(wed_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(wed_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(wed_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(wed_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(wed_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(wed_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(wed_midnight_0300_transit_1$to_id == "thebroadway")
sum(wed_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(thurs_morn_transit_1$to_id == "brucegrovesouth")
sum(thurs_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(thurs_morn_transit_1$to_id == "claphamroadmiddle")
sum(thurs_morn_transit_1$to_id == "danelandwalk")
sum(thurs_morn_transit_1$to_id == "edgwareroadnorth")
sum(thurs_morn_transit_1$to_id == "edgwareroadsouth")
sum(thurs_morn_transit_1$to_id == "highroadmiddle")
sum(thurs_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(thurs_morn_transit_1$to_id == "norwoodroadsouth")
sum(thurs_morn_transit_1$to_id == "oxfordstreetwest")
sum(thurs_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(thurs_morn_transit_1$to_id == "thebroadway")
sum(thurs_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(thurs_afternoon_transit_1$to_id == "brucegrovesouth")
sum(thurs_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(thurs_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(thurs_afternoon_transit_1$to_id == "danelandwalk")
sum(thurs_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(thurs_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(thurs_afternoon_transit_1$to_id == "highroadmiddle")
sum(thurs_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(thurs_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(thurs_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(thurs_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(thurs_afternoon_transit_1$to_id == "thebroadway")
sum(thurs_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(thurs_night_transit_1$to_id == "brucegrovesouth")
sum(thurs_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(thurs_night_transit_1$to_id == "claphamroadmiddle")
sum(thurs_night_transit_1$to_id == "danelandwalk")
sum(thurs_night_transit_1$to_id == "edgwareroadnorth")
sum(thurs_night_transit_1$to_id == "edgwareroadsouth")
sum(thurs_night_transit_1$to_id == "highroadmiddle")
sum(thurs_night_transit_1$to_id == "kenningtonroadmiddle")
sum(thurs_night_transit_1$to_id == "norwoodroadsouth")
sum(thurs_night_transit_1$to_id == "oxfordstreetwest")
sum(thurs_night_transit_1$to_id == "streathamhighroadmiddle")
sum(thurs_night_transit_1$to_id == "thebroadway")
sum(thurs_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(thurs_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(thurs_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(thurs_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(thurs_midnight_0300_transit_1$to_id == "danelandwalk")
sum(thurs_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(thurs_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(thurs_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(thurs_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(thurs_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(thurs_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(thurs_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(thurs_midnight_0300_transit_1$to_id == "thebroadway")
sum(thurs_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(fri_morn_transit_1$to_id == "brucegrovesouth")
sum(fri_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(fri_morn_transit_1$to_id == "claphamroadmiddle")
sum(fri_morn_transit_1$to_id == "danelandwalk")
sum(fri_morn_transit_1$to_id == "edgwareroadnorth")
sum(fri_morn_transit_1$to_id == "edgwareroadsouth")
sum(fri_morn_transit_1$to_id == "highroadmiddle")
sum(fri_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(fri_morn_transit_1$to_id == "norwoodroadsouth")
sum(fri_morn_transit_1$to_id == "oxfordstreetwest")
sum(fri_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(fri_morn_transit_1$to_id == "thebroadway")
sum(fri_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(fri_afternoon_transit_1$to_id == "brucegrovesouth")
sum(fri_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(fri_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(fri_afternoon_transit_1$to_id == "danelandwalk")
sum(fri_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(fri_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(fri_afternoon_transit_1$to_id == "highroadmiddle")
sum(fri_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(fri_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(fri_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(fri_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(fri_afternoon_transit_1$to_id == "thebroadway")
sum(fri_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(fri_night_transit_1$to_id == "brucegrovesouth")
sum(fri_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(fri_night_transit_1$to_id == "claphamroadmiddle")
sum(fri_night_transit_1$to_id == "danelandwalk")
sum(fri_night_transit_1$to_id == "edgwareroadnorth")
sum(fri_night_transit_1$to_id == "edgwareroadsouth")
sum(fri_night_transit_1$to_id == "highroadmiddle")
sum(fri_night_transit_1$to_id == "kenningtonroadmiddle")
sum(fri_night_transit_1$to_id == "norwoodroadsouth")
sum(fri_night_transit_1$to_id == "oxfordstreetwest")
sum(fri_night_transit_1$to_id == "streathamhighroadmiddle")
sum(fri_night_transit_1$to_id == "thebroadway")
sum(fri_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(fri_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(fri_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(fri_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(fri_midnight_0300_transit_1$to_id == "danelandwalk")
sum(fri_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(fri_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(fri_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(fri_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(fri_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(fri_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(fri_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(fri_midnight_0300_transit_1$to_id == "thebroadway")
sum(fri_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sun_morn_transit_1$to_id == "brucegrovesouth")
sum(sun_morn_transit_1$to_id == "claphamhighstreetmiddle")
sum(sun_morn_transit_1$to_id == "claphamroadmiddle")
sum(sun_morn_transit_1$to_id == "danelandwalk")
sum(sun_morn_transit_1$to_id == "edgwareroadnorth")
sum(sun_morn_transit_1$to_id == "edgwareroadsouth")
sum(sun_morn_transit_1$to_id == "highroadmiddle")
sum(sun_morn_transit_1$to_id == "kenningtonroadmiddle")
sum(sun_morn_transit_1$to_id == "norwoodroadsouth")
sum(sun_morn_transit_1$to_id == "oxfordstreetwest")
sum(sun_morn_transit_1$to_id == "streathamhighroadmiddle")
sum(sun_morn_transit_1$to_id == "thebroadway")
sum(sun_morn_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sun_afternoon_transit_1$to_id == "brucegrovesouth")
sum(sun_afternoon_transit_1$to_id == "claphamhighstreetmiddle")
sum(sun_afternoon_transit_1$to_id == "claphamroadmiddle")
sum(sun_afternoon_transit_1$to_id == "danelandwalk")
sum(sun_afternoon_transit_1$to_id == "edgwareroadnorth")
sum(sun_afternoon_transit_1$to_id == "edgwareroadsouth")
sum(sun_afternoon_transit_1$to_id == "highroadmiddle")
sum(sun_afternoon_transit_1$to_id == "kenningtonroadmiddle")
sum(sun_afternoon_transit_1$to_id == "norwoodroadsouth")
sum(sun_afternoon_transit_1$to_id == "oxfordstreetwest")
sum(sun_afternoon_transit_1$to_id == "streathamhighroadmiddle")
sum(sun_afternoon_transit_1$to_id == "thebroadway")
sum(sun_afternoon_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sun_night_transit_1$to_id == "brucegrovesouth")
sum(sun_night_transit_1$to_id == "claphamhighstreetmiddle")
sum(sun_night_transit_1$to_id == "claphamroadmiddle")
sum(sun_night_transit_1$to_id == "danelandwalk")
sum(sun_night_transit_1$to_id == "edgwareroadnorth")
sum(sun_night_transit_1$to_id == "edgwareroadsouth")
sum(sun_night_transit_1$to_id == "highroadmiddle")
sum(sun_night_transit_1$to_id == "kenningtonroadmiddle")
sum(sun_night_transit_1$to_id == "norwoodroadsouth")
sum(sun_night_transit_1$to_id == "oxfordstreetwest")
sum(sun_night_transit_1$to_id == "streathamhighroadmiddle")
sum(sun_night_transit_1$to_id == "thebroadway")
sum(sun_night_transit_1$to_id == "wandsworthroadsouth")
```

```{r}
sum(sun_midnight_0300_transit_1$to_id == "brucegrovesouth")
sum(sun_midnight_0300_transit_1$to_id == "claphamhighstreetmiddle")
sum(sun_midnight_0300_transit_1$to_id == "claphamroadmiddle")
sum(sun_midnight_0300_transit_1$to_id == "danelandwalk")
sum(sun_midnight_0300_transit_1$to_id == "edgwareroadnorth")
sum(sun_midnight_0300_transit_1$to_id == "edgwareroadsouth")
sum(sun_midnight_0300_transit_1$to_id == "highroadmiddle")
sum(sun_midnight_0300_transit_1$to_id == "kenningtonroadmiddle")
sum(sun_midnight_0300_transit_1$to_id == "norwoodroadsouth")
sum(sun_midnight_0300_transit_1$to_id == "oxfordstreetwest")
sum(sun_midnight_0300_transit_1$to_id == "streathamhighroadmiddle")
sum(sun_midnight_0300_transit_1$to_id == "thebroadway")
sum(sun_midnight_0300_transit_1$to_id == "wandsworthroadsouth")
```
